Strong lensing selection effects

### 2022-06-29 paper/seleff.tex
intro and composite grid

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
    {
There are selection effects. They are important.
}
  % aims heading (mandatory)
   {
How important?
} 
   % methods heading (mandatory)
   {
I simulate lenses.
}
% results heading (mandatory)
   {
Results.
}
  % conclusions heading (optional), leave it empty if necessary 
   {
I conclude.
}
   \keywords{
             Gravitational lensing: strong --
             Galaxies: fundamental parameters
               }

@@

>>>>

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
    {
There are selection effects. They are important.
}
  % aims heading (mandatory)
   {
How important?
} 
   % methods heading (mandatory)
   {
I simulate lenses.
}
% results heading (mandatory)
   {
Results.
}
  % conclusions heading (optional), leave it empty if necessary 
   {
I conclude.
}
   \keywords{
             Gravitational lensing: strong 
               }

@@

Strong gravitational lensing is a powerful tool for studying galaxies and cosmology.
%Strongly lensed images enable us to make very precise measurements of the mass 
Strong lenses have been used to probe the mass structure of massive galaxies \citep{Aug++10, ORF14, Son++15, Sha++21}, to detect substructure \citep{Veg++12, Hez++16, Nie++20}, to carry out detailed studies of magnified star-forming galaxies \citep{Jon++13}, and to measure the expansion rate of the universe with time delays \citep[see][for a review]{T+M16}.

Strong lenses, however, are a biased subset of the general population of galaxies and background sources.
A necessary condition for a galaxy to act as a strong lens with respect to a given source is that its projected surface mass density $\Sigma(\boldsymbol\theta)$ must be larger than the critical surface mass density for lensing $\Sigma_{\mathrm{cr}}$ at least one position $\boldsymbol\theta$ \citep{SEF92}.
This condition excludes objects with a very diffuse mass distribution from the population of lenses.
In general, galaxies with a higher concentration of mass are more likely to be strong lenses, and are therefore over-represented in lens samples.

The distribution of background source properties is also affected by

In order for a galaxy to act as a strong lens with respect to a given source, it is necessar
Galaxies with a higher concentration of mass are more likely to be strong lenses
Strong lensing is a rare phenomenon
